### 2023-01-19 paper.tex
Remove authors for double blind review

	\author{\IEEEauthorblockN{Carl Egge}
		\IEEEauthorblockA{\textit{Institute for Data Engineering} \\
			\textit{Hamburg University of Techology}\\
			Hamburg, Germany \\
			email address or ORCID}
		\and
		\IEEEauthorblockN{Avik Banerjee}
		\IEEEauthorblockA{\textit{Institute for Data Engineering} \\
			\textit{Hamburg University of Technology}\\
			Hamburg, Germany \\
			email address or ORCID}
		\and
		\IEEEauthorblockN{Stefan Schulte}
		\IEEEauthorblockA{\textit{Institute for Data Engineering} \\
			\textit{Hamburg University of Technology}\\
			Hamburg, Germany \\
			email address or ORCID}
		\and
			\IEEEauthorblockN{Michael Schröder}
		\IEEEauthorblockA{\textit{Institute of Information Systems Engineering} \\
			\textit{Technische Universität Wien}\\
			Vienna, Austria \\
			email address or ORCID}
		\and
		\IEEEauthorblockN{Jürgen Cito}
		\IEEEauthorblockA{\textit{Institute of Information Systems Engineering} \\
			\textit{Technische Universität Wien}\\
			Vienna, Austria \\
			email address or ORCID}}

>>>>

%	\author{\IEEEauthorblockN{Carl Egge}
%		\IEEEauthorblockA{\textit{Institute for Data Engineering} \\
%			\textit{Hamburg University of Techology}\\
%			Hamburg, Germany \\
%			email address or ORCID}
%		\and
%		\IEEEauthorblockN{Avik Banerjee}
%		\IEEEauthorblockA{\textit{Institute for Data Engineering} \\
%			\textit{Hamburg University of Technology}\\
%			Hamburg, Germany \\
%			email address or ORCID}
%		\and
%		\IEEEauthorblockN{Stefan Schulte}
%		\IEEEauthorblockA{\textit{Institute for Data Engineering} \\
%			\textit{Hamburg University of Technology}\\
%			Hamburg, Germany \\
%			email address or ORCID}
%		\and
%			\IEEEauthorblockN{Michael Schröder}
%		\IEEEauthorblockA{\textit{Institute of Information Systems Engineering} \\
%			\textit{Technische Universität Wien}\\
%			Vienna, Austria \\
%			email address or ORCID}
%		\and
%		\IEEEauthorblockN{Jürgen Cito}
%		\IEEEauthorblockA{\textit{Institute of Information Systems Engineering} \\
%			\textit{Technische Universität Wien}\\
%			Vienna, Austria \\
%			email address or ORCID}}
